Storm Surges

### 2014-04-24 RoughWork/manuscript.tex
Updated descritpion of vertical grid spacing.

The curvilinear orthogonal numerical grid is divided into 400 by 900 by 40 grid cells, which results in an almost uniform horizontal resolution with grid spacing approximately 400 m by 500 m. The 40 vertical $z$-levels are stretched gradually in order to achieve higher resolution in the surface layer, with approximately 1 m vertical grid spacing down to about 20 m in depth. At the bottom boundary, partial $z$-levels are utilized in order to limit large changes in bathymetry across grid cells \citep{madec2008nemo}.

>>>>

The curvilinear orthogonal numerical grid is divided into 400 by 900 by 40 grid cells, which results in an almost uniform horizontal resolution with grid spacing approximately 400 m by 500 m. The 40 vertical $z$-levels are stretched gradually in order to achieve higher resolution in the surface layer, with 1 m vertical grid spacing down to about 10 m in depth. Below 10m the grid is stretched gradually with a maxmimum grid spacing of 27 m at the lowest layer. At the bottom boundary, partial $z$-levels are utilized in order to limit large changes in bathymetry across grid cells \citep{madec2008nemo}.
